\section{Introduction}

This project is focused on integrating AI-powered Large Language Models (LLMs) with the NAO6 humanoid robot to enable interactive and engaging conversations. A framework is being developed to facilitate seamless communication between the NAO6 robot and AI-driven services using IU South Bend’s Computer Science Linux servers.

To achieve this, a backend infrastructure is being implemented using Docker containers to manage full-stack JavaScript development, APIs for Ollama LLMs, and Google's speech recognition libraries. This approach has been chosen to ensure modularity, scalability, and ease of deployment. 

A key aspect of the project is enhancing the NAO6’s speech recognition capabilities. Since the built-in speech recognition of the NAO6 robot has been found to be unreliable, an external speech-to-text module is being integrated using Python and Google’s Speech-to-Text API. This module will be deployed as a dedicated Docker container and will communicate securely within the backend network.

Beyond voice interaction, additional functionality is planned, including a browser-based interface for managing AI models and robot controls. Future improvements will include encrypted communication, customizable chatbot personalities, and the ability to switch between different LLMs for tailored interactions.

In this document, the system’s core functionalities, backend architecture, software interfaces, and expected behavior are outlined to provide a comprehensive overview of the development process and planned enhancements.
