\section{Key Technologies}

\subsection{Key Technologies and Innovations}

\begin{itemize}
  \item \textbf{Container Technology}

    In this project we are planning to use Docker as a platform to host
    our services. Containerizing our services is the main reason we
    chose Docker. With containers we can develop on our personal machine
    and then deploy to another machine like the cloud without making any
    special configurations. There are other desirable features like
    container networking, creating multiple containers from a single
    compose file, and monitoring the health of your docker containers.

  \item \textbf{LLM}

    Ollama will be used to host our large language model (LLM) within
    docker. Ollama includes an API backend that can be used to chat with
    the large language model and manage Ollama's services like
    installing, removing, and swapping to other large language models
    (Like Deepseek R1, Meta's llama, and more models).

  \item \textbf{Web Application}

    Node.js will be used to host our web application and API server in
    one container. This API server will be used as a ``middleman'' to
    receive requests and send responses from and to the web application
    and the \naosix\ robot. The web application will control which
    application the \naosix\ robot is running, it also shows which model
    is being run on the Ollama server. The user can change Ollama's LLM
    from the web application as well.

  \item \textbf{Humanoid Robot}

    The application will be deployed directly on the \naosix\ robot,
    allowing it to engage in conversations with users while performing
    interactive animations. The robot will communicate with the backend
    of the application through a Wi\nobreakdash-Fi connection.
\end{itemize}

\subsection{Required Hardware and Software}

The services that we are planning to host on Docker are Ollama and
Node.js. Ollama is going to be used for hosting large language models
(LLMs) and includes an API server to manage and talk to these large
language models. Node.js will be used to host our web application and
API server in one container. The programming language that the API
server will use is JavaScript and will be used as a ``middleman'' to
receive requests from and send responses to the web application and the
\naosix\ robot. The web application will control which application the
\naosix\ robot is running, it also shows which model is being run on the
Ollama server. The user can change Ollama's LLM from the web application
as well. For the \naosix\ robot we are planning to implement a Python
program that makes the robot able to send requests to and receive
responses from the API server. \\

Hardware Needed:

\begin{itemize}
  \item \naosix\ Robot
  \item Web Server
  \item Computer with GPU
\end{itemize}

Software Needed:

\begin{itemize}
  \item Any operating system
  \item Docker engine
  \item Ollama docker container
  \item Node.js docker container
  \item Choreographe, the programming software of \naosix
  \item Python
\end{itemize}
